### 2017-04-07 pubs/hcar16.2/AutoparallelizingPureFunc-KA.tex
new HCAR entry w/ pointer to Loren paper and hinting at David program analysis

\documentclass[DIV16,twocolumn,10pt]{scrreprt}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage[final]{hcar}

%include polycode.fmt

\begin{document}

\begin{hcarentry}{Auto-parallelizing Pure Functional Language System}
\report{Kei Davis}
\status{active}
\participants{Dean Prichard, David Ringo, Loren Anderson, Jacob Marks}
\makeheader

%(WHAT IS IT?)

The main project goal is the demonstration of a light-weight, higher-order,
polymorphic, pure functional language implementation in which we can
experiment with automatic parallelization strategies, varying degrees of
default function and constructor strictness.  A secondary goal is to
experiment with mechanisms for transparent fault tolerance.
%
We do not consider speculative or eager evaluation, or semantic strictness
inferred by program analysis, so potential parallelism is dictated by the
specified degree of default strictness and any strictness annotations.

Our approach is similar to that of the
\href{https://dl.acm.org/citation.cfm?id=2503779}{Intel Labs Haskell Research
  Compiler}: to use GHC as a front-end to generate STG (or Core), then exit to
our own back-end compiler that is itself written in Haskell.  As in their case
we do not attempt to use the GHC runtime.  Our implementation is
\emph{light-weight} in that we are not attempting to support or recreate the
vast functionality of GHC and its runtime.  This approach is also similar to
\href{http://www.cse.unsw.edu.au/~pls/thesis/dons-thesis.ps.gz}{Don Stewart's}
except that we generate C instead of Java.

%(WHAT IS ITS STATUS? / WHAT HAS HAPPENED SINCE LAST TIME?)
\subsubsection*{Current Status}
Currently we have a fully functioning serial implementation and a primitive
proof-of-design parallel implementation.

%(CAN OTHERS GET IT?)

%(WHAT ARE THE IMMEDIATE PLANS?)
\subsubsection*{Immediate Plans}

We are currently developing a more realistic parallel runtime.
%
Bridging the gap between GHC STG (or Core) to our STG representation will be
undertaken starting June 2016.  An instrumentation framework will be developed
in summer 2016.

\FurtherReading
 A \href{https://github.com/losalamos/APPFL}{project web site} is under construction.

@@

\emph{\bfseries The application process requires a bit of work so don't leave
  enquiries until the last day/month.}\\

\begin{tabular}{l|l}
Term & Application Deadline \\
\hline
Summer 2016  & Closed \\
Fall 2016    & May 31, 2016 \\
Spring 2017  & Approx. July 2016 \\
Summer 2017  & Approx. January 2017 \\
Fall 2017    & Approx. May 2017
\end{tabular}\\

@@

\end{hcarentry}
\end{document}

>>>>

% AutoparallelizingPureFunc-KA.tex
\begin{hcarentry}[new]{Auto-parallelizing Pure Functional Language System}
\report{Kei Davis}%05/16
\status{active}
\participants{Dean Prichard, David Ringo, Loren Anderson}
\makeheader

The main project goal is the demonstration of a light-weight, higher-order,
polymorphic, pure functional language implementation in which we can
experiment with automatic parallelization strategies and varying degrees of
default function and constructor strictness.  A secondary goal is to
experiment with mechanisms for transparent fault tolerance.

We do not consider speculative or eager evaluation, or semantic strictness
inferred by program analysis, so potential parallelism is dictated by the
specified degree of default strictness and any strictness annotations.

Our approach is similar to that of the
\href{https://dl.acm.org/citation.cfm?id=2503779}{Intel Labs Haskell
Research Compiler}, using GHC as a front-end to generate STG, then
exit to our own back-end compiler.  As in their case we do not attempt to use
the GHC runtime.  Our implementation is \emph{light-weight} in that we are not
attempting to support or recreate the vast functionality of GHC and its
runtime.  This approach is also similar to
\href{http://www.cse.unsw.edu.au/~pls/thesis/dons-thesis.ps.gz}{Don Stewart's}
except that we generate C instead of Java.

\subsubsection*{Current Status}
Currently we have a fully functioning serial implementation and a primitive
proof-of-design parallel implementation.  The most recent major development
was the ``bridge'' between GHC and our system.  Thus we can now compile and run
Haskell programs with simple primitive and algebraic data types.

\subsubsection*{Immediate Plans}

We are currently developing a more realistic parallel runtime.  Tentatively
the fault tolerance mechanism is scheduled as a Master's thesis project starting
summer 2017.

@@

\emph{\bfseries The application process requires a bit of work so don't leave
enquiries until the last day/month.}  Dates for terms beyond summer 2017 are
best guesses based on prior years.\\

\begin{tabular}{l||l|l}
Term & Application Opening & Deadline \\
\hline
Summer 2017  & Open & Jan 2017 \\
Fall 2017    & Jan 2017 & May 2017 \\
Spring 2018  & May 2017 & Jul 2017 \\
\end{tabular}\\

@@

\FurtherReading
Email me as above for the Trends in Functional Programming 2016 paper
about this project.

\end{hcarentry}

### 2017-04-07 pubs/hcar17.1/AutoparallelizingPureFunc-KA.tex
new HCAR entry w/ pointer to Loren paper and hinting at David program analysis

% AutoparallelizingPureFunc-KA.tex
\begin{hcarentry}[new]{Auto-parallelizing Pure Functional Language System}
\report{Kei Davis}%05/16
\status{active}
\participants{Dean Prichard, David Ringo, Loren Anderson}
\makeheader

The main project goal is the demonstration of a light-weight, higher-order,
polymorphic, pure functional language implementation in which we can
experiment with automatic parallelization strategies and varying degrees of
default function and constructor strictness.  A secondary goal is to
experiment with mechanisms for transparent fault tolerance.

We do not consider speculative or eager evaluation, or semantic strictness
inferred by program analysis, so potential parallelism is dictated by the
specified degree of default strictness and any strictness annotations.

Our approach is similar to that of the
\href{https://dl.acm.org/citation.cfm?id=2503779}{Intel Labs Haskell
Research Compiler}, using GHC as a front-end to generate STG, then
exit to our own back-end compiler.  As in their case we do not attempt to use
the GHC runtime.  Our implementation is \emph{light-weight} in that we are not
attempting to support or recreate the vast functionality of GHC and its
runtime.  This approach is also similar to
\href{http://www.cse.unsw.edu.au/~pls/thesis/dons-thesis.ps.gz}{Don Stewart's}
except that we generate C instead of Java.

\subsubsection*{Current Status}
Currently we have a fully functioning serial implementation and a primitive
proof-of-design parallel implementation.  The most recent major development
was the ``bridge'' between GHC and our system.  Thus we can now compile and run
Haskell programs with simple primitive and algebraic data types.

@@

We are currently developing a more realistic parallel runtime.  Tentatively
the fault tolerance mechanism is scheduled as a Master's thesis project starting
summer 2017.

@@

\emph{\bfseries The application process requires a bit of work so don't leave
enquiries until the last day/month.}  Dates for terms beyond summer 2017 are
best guesses based on prior years.\\

\begin{tabular}{l||l|l}
Term & Application Opening & Deadline \\
\hline
Summer 2017  & Open & Jan 2017 \\
Fall 2017    & Jan 2017 & May 2017 \\
Spring 2018  & May 2017 & Jul 2017 \\
\end{tabular}\\

\noindent Email me at kei (at) lanl (dot) gov if interested in more
information, and feel free to pass this along. \\

\FurtherReading
Email me as above for the Trends in Functional Programming 2016 paper
about this project.

\end{hcarentry}

>>>>

% AutoparallelizingPureFunc-KA.tex
\begin{hcarentry}[updated]{Auto-parallelizing Pure Functional Language System}
\report{Kei Davis}%11/16
\status{active}
\participants{Dean Prichard, David Ringo, Loren Anderson, Jacob Marks}
\makeheader

The main project goal is the demonstration of a light-weight, higher-order,
polymorphic, pure functional language implementation with which we can
experiment with automatic parallelization strategies, varying degrees of
default function and constructor strictness, and lightweight instrumentation.

We do not consider speculative or eager evaluation, but do plan to infer
strictness by program analysis, so potential parallelism is dictated by the
specified degree of default strictness, language constructs for parallelism,
and program analysis.

Our approach is similar to that of the
\href{https://dl.acm.org/citation.cfm?id=2503779}{Intel Labs Haskell
Research Compiler}: we use GHC as a front-end to generate STG, then
exit to our own back-end compiler.  As in their case we do not attempt to use
the GHC runtime.  Our implementation is \emph{light-weight} in that we are not
attempting to support or recreate the vast functionality of GHC and its
runtime.  This approach is also similar to
\href{http://www.cse.unsw.edu.au/~pls/thesis/dons-thesis.ps.gz}{Don Stewart's}
except that we generate C instead of Java.

\subsubsection*{Current Status}
Currently we have a fully functioning serial implementation and a primitive
proof-of-design parallel implementation. The most recent major development
was the bridge between GHC and our system. Thus we can now compile and run
Haskell programs with simple primitive and algebraic data types.

Additionally, we have developed a new strictness analysis technique that will
be incorporated into the compiler.  We'll miss the Static Analysis Symposium
2017 submission deadline, unfortunately.

@@

We are currently developing a more realistic parallel runtime.
The implementation of the strictness analysis is scheduled as a Master's thesis project
starting May 2017.

@@

\emph{\bfseries The application process requires a bit of work so don't leave
enquiries until the last day/month.}  Dates for terms beyond fall 2017 are
best guesses based on prior years.\\

\begin{tabular}{l||l||l}
Term & Application & Deadline \\
     & Opening &  \\
\hline
Fall 2017    & Open      & May 31 2017 \\
Spring 2018  & July 2017 & Oct 2017 \\
Summer 2018  & Oct 2017  & Jan 2018 \\
\end{tabular}\\

\noindent Email kei (at) lanl (dot) gov if interested in more
information, and feel free to pass this along. \\

\FurtherReading
Email same address as above for the Trends in Functional Programming 2016
paper about this project.

Intern Loren Anderson did an interesting Haskell exercise while here for this
\href{http://ijmcs.future-in-tech.net/11.1/R-Anderson.pdf}{mathematics paper}.
\end{hcarentry}
